Effects of CHILDREN's programs

### 2020-02-26 paper.Rnw
xxx
ghj

\section{Formal requirements}
all important information on title page, maybe use template\\
always name sources of tables and graphs\\
have to cite data sets\\

@@

<<GrantsRegressions, echo=FALSE, results='asis', message=FALSE>>=

lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds") #outlier meals
lm_ts_o = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds")#outlier trips 
lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals
lm_ts_i = readRDS("./ANALYSIS/Tables/tripsNo_sub_IM.lm.Rds")#imputetrips

texreg(list(lm_ms, lm_ts, lm_ms_o, lm_ts_o, lm_ms_i, lm_ts_i), caption = "Grants Regressions", custom.model.names = c("MealsNo", "Trips No", "Meals No", "Trips No", "Meals No", "Trips No"))
@
The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed. 
(DESCRIBE RESULTS) (COMPARE TO SUMMARY STATISTICS)

\subsection{Variables of interest: Health variables}

@@

<<HealthRegressions, echo=FALSE, results='asis', message=FALSE>>=

#scaled regressions

lm_lDGE = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled.lm.Rds")
lm_dDGE = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled.Rds")
lm_aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")
lDGE_i = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled.lm.Rds")
dDGE_i = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_IM_scaled.lm.Rds")
aDGE_i = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_IM_scaled.lm.Rds")

#expanded model less ill

lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
elDGE_i = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled.Rds")

texreg(list(lm_lDGE, lm_dDGE, lm_aDGE, lDGE_i, dDGE_i, aDGE_i), caption = "Health Outcome Regressions", custom.model.names = c("LessIll", "DietaryKnowledge", "AppreciateHealthy","LessIll", "DietaryKnowledge", "AppreciateHealthy"))
@

@@

<<ChanceEqualityRegressions, echo=FALSE, results='asis', message=FALSE>>=

lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
lm_ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardized
lm_ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardized 
tss = readRDS("./ANALYSIS/Tables/selfworthTrips_scaled.Rds")
tds = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_scaled.lm.Rds")

texreg(list(lm_s, lm_d, ts, td, lm_ss, lm_ds, tss, tds), caption = "Equal Opportunities Regressions", custom.model.names = c("selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills" ))
@

<<ChanceEqualityRegressionsImpute, echo=FALSE, results='asis', message=FALSE>>=

sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
ssI = readRDS("./ANALYSIS/Tables/selfworth_IM_scaled.lm.Rds") #standardized
dsI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM_scaled.lm.Rds") #standardized 
tssI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM_scaled.lm.Rds")
tdsI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM_scaled.lm.Rds")

texreg(list(sI, dI, tsI, tdI, ssI, dsI, tssI, tdsI), caption = "Equal Opportunities Regressions, imputed data", custom.model.names = c("selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills" ))
@

@@

xtable(partition_trips,
                               #digits = c(0, 0, 1, 1, 0, 0),
          caption = "Partition of outcomes, Trips"
          #align = "lmmm"
          )
print(partition_meals, partition_trips, include.rownames = FALSE)
@

>>>>

\section{Formal requirements}
all important information on title page, maybe use template\\
always name sources of tables and graphs\\
have to cite data sets\\
latin number pages\\

@@

<<GrantsRegressions Lunch, echo=FALSE, results='asis', message=FALSE>>=

lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds") #outlier meals
lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals

texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Regression Results: Number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
@

<<GrantsRegressions Trips, echo=FALSE, results='asis', message=FALSE>>=
lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
lm_ts_o = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds") #outlier trips
lm_ts_i = readRDS("./ANALYSIS/Tables/tripsNo_sub_IM.lm.Rds") #imputetrips

texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)

@
\subsection{Variables of interest: Health variables}

@@

<<HealthRegressions_LessIll, echo=FALSE, results='asis', message=FALSE>>=

lDGE = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled.lm.Rds")
#extraweighted
lDGEw = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled_weighted.lm.Rds")
#standardized
lDGE_i = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled.lm.Rds")
#extraweighted
lDGE_iw = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled_weighted.lm.Rds")

texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw), caption = "Regression Results: Less Ill", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8)
@

<<HealthRegressions_DietaryKnowledge, echo=FALSE, results='asis', message=FALSE>>=
dDGE = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled.Rds")
dDGEw = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled_weighted.Rds")
dDGE_i = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_IM_scaled.lm.Rds")
dDGE_iw = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_IM_scaled_weighted.lm.Rds")

texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw), caption = "Regression Results: Dietary Knowledge", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8)
@

<<HealthRegressions_AppreciateHealthy, echo=FALSE, results='asis', message=FALSE>>=
aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")
aDGEw = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled_weighted.Rds")
aDGE_i = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_IM_scaled.lm.Rds")
aDGE_iw = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_IM_scaled_weighted.lm.Rds")

texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw), caption = "Regression Results: Appreciate Healthy", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8)
@

@@

<<SelfworthRegressions, echo=FALSE, results='asis', message=FALSE>>=

ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardizedweighted
tss = readRDS("./ANALYSIS/Tables/selfworthTrips_scaled.Rds")#sw
ssI = readRDS("./ANALYSIS/Tables/selfworth_IM_scaled.lm.Rds") #standardized
tssI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM_scaled.lm.Rds")

texreg(list(ss, tss, ssI, tssI ), caption = "Regression Results: Selfworth", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8)
@

<<DayToDaySkillsRegressions, echo=FALSE, results='asis', message=FALSE>>=
ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardizedweigh
tds = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_scaled.lm.Rds")
dsI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM_scaled.lm.Rds") 
tdsI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM_scaled.lm.Rds")

texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8)
@

@@

xtable(partition_trips,
                               #digits = c(0, 0, 1, 1, 0, 0),
          caption = "Partition of outcomes, Trips"
          #align = "lmmm"
          )
print(partition_meals, partition_trips, include.rownames = FALSE)
@
\subsection{A3: OLS Regressions}

#normal weights selfworth& subsidiy
<<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=

lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
@

<<lessIll_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
#expanded model less ill

lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
lm_elDGEw = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled_weighted.Rds")
elDGE_iw = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled_weighted.Rds")
@
